Analysis of Programming Students' Prompts to Identify Interactions Patterns with Generative AI

### 2024-09-25 CSEDU2025/Paper.tex
update

\subsection*{Lack of Interleaving}

% Interleaving
Interleaving, a technique that involves alternating the conversation among
different types of categories.

% Eglington, L. G., & Kang, S. H. (2017). Interleaved presentation benefits
% science category learning. Journal of Applied Research in Memory and Cognition,
% 6, 475-485

To highlight the low incidence of interleaving, we conducted an analysis to
identify blocks of four or more consecutive messages classified within the same
category. The results showed that approximately 36\% of the messages are
distributed across 22 blocks. Specifically, the Debugging Help category contains
10 blocks of four or more messages, Conceptual Question has seven blocks,
Multiple Choice has three blocks, while Code Snippet and Complete Solution each
have one block.

Interestingly, when expanding the analysis to blocks of three consecutive
messages, the percentage of messages grouped within blocks of the same category
increases to about 45% of the total. It is also worth noting that three
categories – Student Correction, Language Change, and Uncategorized – did not
form any sequential blocks. The figure \ref{fig:graph2} shows 15 conversations,
one clear example of blocks can be observed in conversation eight which contains
two blocks of Multiple Choice questions. Another example is conversation 10,
with the entire conversation forming a one block of Conceptual Questions.

>>>>

\subsection*{Interleaving}

% Interleaving

Intervealing is a study strategy that involves mixing or alternating different
topics or problems within a single learning session. This
approach has been shown to be useful for promoting long-term learning and
improving the application of knowledge in other situations \cite{Rivers21}.

When analyzing the classification of messages in conversations, we identified
the presence of sequences of messages belonging to the same category, that it
could suggest a low occurrence of interleaving. To better assess the extent of
these sequences, we calculated the percentage of messages that were part of
repeated blocks.

Considering blocks with at least three messages, we observed that 56.2\% of the
students' prompts were grouped into some sequence. When analyzing blocks with a
minimum of 4 messages, we found that 47.5\% of the prompts were part of
continuous sequences. These results indicate a moderate incidence of
interleaving among the students' messages.

To illustrate the presence of blocks the Figure \ref{fig:graph2} presents
examples of conversations and their classification. In Conversation 2, the
student alternates messages among Code Snippet, Debugging Help and Conceptual
Question, showing an tendency of interleaving between practical and theoretical
perspectives. In contrast, in Conversation 10, the student focused on a single
block of Conceptual Question. Although the focus was on understanding a
theoretical concept, this conversation tended not to promote interleaving, due
to the absence of alternation between different types of tasks.
